### 2018-04-23 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
Goodness of fit notes update
Update of all files to shorten preamble
Tidied to work with all linux systems
Notes Update
Fixed incorrect word

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{enumitem}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S3}
\rfoot{Page \thepage}

@@

@@

$$H_0:\textrm{The binomial distribution is a suitable model}$$
$$H_1:\textrm{The binomial distribution is a suitable model}$$

@@

\item $H_1$ is that they are independent

>>>>

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - S3}

%File specific Preamble
\usepackage{multirow} %Merge cells in tables

@@

$$\sum\frac{(O_i-E_i)^2}{E_i} \textrm{can be rewritten as  } \quad \Bigg(\sum\frac{O^2_i}{E_i}\Bigg)-N$$

@@

$$H_0:\textrm{The uniform distribution is a suitable model}$$
$$H_1:\textrm{The uniform distribution is a suitable model}$$

@@

\item $H_1$ is that they are not independent
